Supplementary Materials And Methods

### 2020-11-05 Supplementary_mat_met.Rmd
liftover data added, cosmetic changes

#After we uploaded this file to UCSC Liftover site, the output files  lift19_del (deleted regions on the HG38 genome build) and hg38clashcomp (new locations of the genes on HG38) were downloaded

lift19_del <- read_tsv("deleted_lift19.txt")
colnames(lift19_del)[1] <- "chromosome_loc"

lift19_del <- lift19_del %>%
  dplyr::filter(startsWith(chromosome_loc, "chr")) %>%
  separate(chromosome_loc, c("Chr", "End"), "-", remove = TRUE) %>%
  separate(Chr, c("Chr", "Start"), ":", remove = TRUE)

lift19_del$Start <- as.numeric(lift19_del$Start)
lift19_del$End <- as.numeric(lift19_del$End)

@@

clashelwakfinal <-clashelwakfinal%>%
  mutate(Chromosome = paste0("chr",chromosome_name, "")) %>%
  dplyr::anti_join(lift19_del, by = c("Chromosome"="Chr",
                                      "start_position"="Start",
                                      "end_position"="End"))

hg38clash <- read.delim("hg38clashcomp.txt", header = FALSE, stringsAsFactors = FALSE)

# adding new location information:

clashelwakfinal <- clashelwakfinal %>% 
  bind_cols(hg38clash)

colnames(clashelwakfinal)[18] <- "HG38build_loc"

clashelwakfinal <- clashelwakfinal %>%
  dplyr::mutate(Genom_build= rep("hg19"))

@@

clashelwakfinal <- clashelwakfinal %>% 
  dplyr::select(cluster=seq_ID, 
                chromosome = Chromosome,
                start_position, end_position, strand,
                hgnc_symbol = Hugo_Symbol,
                Ensembl_Gene_Id, Ensembl_Transcript_Id,
                target_seq = mRNA_seq_extended,
                miRNA = Name,
                miR_seq = miRNA_seq,
                seed_type,
                seed_type2 = seed_basepairs,
                seed_type3 = folding_class,
                Energy = folding_energy,
                HG38build_loc, Genom_build, region)

clashelwakfinal$strand <- as.character(clashelwakfinal$strand)

str(clashelwakfinal)
```

@@

deleted_lift18 <- read_tsv("deleted_lift18.txt")

colnames(deleted_lift18)[1] <- "Chromosome_loc"

deleted_lift18 <- deleted_lift18 %>%
  dplyr::filter(startsWith(Chromosome_loc, "chr")) %>%
  separate(Chromosome_loc, c("Chr", "End"), "-", remove = TRUE) %>%
  separate(Chr, c("Chr", "Start"), ":", remove = TRUE)

deleted_lift18$Start <- as.numeric(deleted_lift18$Start)
deleted_lift18$End <- as.numeric(deleted_lift18$End)

@@

hg38clearclip<- read.delim("hg38clearclip.txt", header = FALSE, stringsAsFactors = FALSE)

clearclipfinal <- clearclipfinal %>% 
  bind_cols(hg38clearclip)

colnames(clearclipfinal)[28] <- "HG38build_loc"

# adding new location information:

clearclipfinal <- clearclipfinal %>%
  dplyr::mutate(Genom_build= rep("hg18"))

clearclipfinal %>%
  dplyr::select(cluster=cluster.ID, chromosome = chr, start_position, 
                end_position, strand = strand.y, hgnc_symbol, 
                Ensembl_Gene_Id =ensembl_gene_id, 
                Ensembl_Transcript_Id =ensembl_transcript_id, 
                target_seq = target.map, miRNA, 
                miR_seq = miR.map, 
                seed_type = 'seed match', Energy = MFE, 
                HG38build_loc, Genom_build, region) -> clearclipfinal

>>>>

#In liftover site, Original Assembly was chosen as hg19 and New Assebly was chosen as hg38. After we uploaded "lift19.txt" file to UCSC Liftover site, the output "View Conversions" was downloaded as hg38clashcomp (new locations of the genes on HG38), "Display failure file" was download as "lift19_del.txt" (deleted regions on the HG38 genome build)

lift19_del <- read_tsv("figure_manuscript/lift19_del.txt", 
                       col_names = FALSE, 
                       comment = "#") %>% 
  rename(chromosome_loc = X1) %>% 
  dplyr::filter(str_starts(chromosome_loc, "chr")) %>% 
  separate(chromosome_loc, c("Chr", "End"), "-", remove = TRUE) %>%
  separate(Chr, c("Chr", "Start"), ":", remove = TRUE) %>% 
  mutate(Start=as.numeric(Start),
         End=as.numeric(End))

@@

clashelwakfinal <- clashelwakfinal %>%
  mutate(Chromosome = paste0("chr",chromosome_name, "")) %>%
  dplyr::anti_join(lift19_del, by = c("Chromosome"="Chr",
                                      "start_position"="Start",
                                      "end_position"="End"))
# adding new location information:

clashelwakfinal <- clashelwakfinal %>% 
  bind_cols(read_tsv("figure_manuscript/hg38clashcomp.txt", 
                      col_names = FALSE))

@@

clashelwakfinal <- clashelwakfinal %>% 
  rename(HG38build_loc = X1) %>% 
  mutate(Genom_build="hg19") %>% 
  dplyr::select(cluster=seq_ID, 
                chromosome = Chromosome,
                start_position, end_position, strand,
                hgnc_symbol = Hugo_Symbol,
                Ensembl_Gene_Id, Ensembl_Transcript_Id,
                target_seq = mRNA_seq_extended,
                miRNA = Name,
                miR_seq = miRNA_seq,
                seed_type,
                seed_type2 = seed_basepairs,
                seed_type3 = folding_class,
                Energy = folding_energy,
                HG38build_loc, Genom_build, region) %>% 
  mutate(strand = as.character(strand))
```

@@

deleted_lift18 <- read_tsv("figure_manuscript/lift18_del.txt",
                           comment = "#",
                           col_names = FALSE) %>% 
  rename(Chromosome_loc = X1) %>% 
  dplyr::filter(str_starts(Chromosome_loc, "chr")) %>%
  separate(Chromosome_loc, c("Chr", "End"), "-", remove = TRUE) %>%
  separate(Chr, c("Chr", "Start"), ":", remove = TRUE) %>% 
  mutate(Start = as.numeric(Start),
         End = as.numeric(End))

@@

hg38clearclip <- read_tsv("figure_manuscript/hg38clearclip.txt",
                          col_names = FALSE)

# adding new location information:
clearclipfinal <- clearclipfinal %>% 
  bind_cols(hg38clearclip) %>% 
  rename(HG38build_loc = X1) %>% 
  mutate(Genom_build="hg18") %>%
  dplyr::select(cluster=cluster.ID, chromosome = chr, start_position, 
                end_position, strand = strand.y, hgnc_symbol, 
                Ensembl_Gene_Id =ensembl_gene_id, 
                Ensembl_Transcript_Id =ensembl_transcript_id, 
                target_seq = target.map, miRNA, 
                miR_seq = miR.map, 
                seed_type = 'seed match', Energy = MFE, 
                HG38build_loc, Genom_build, region)
